---
title: "Lab 6: Team All Stars"
author: "Johnny Tamanaha, Emily Archambault, Eugene Miller, Kaiyuan Fan, Jingzhi Zhang"
date: "10/4/2019"
output: html_document
---

```{r, setup, message = FALSE, echo = FALSE, warning = FALSE}
library(tidyverse)
library(corrplot)
library(quantreg)
library(hexbin)
COflights <- read_csv("https://files.osf.io/v1/resources/3z5as4pej8/providers/osfstorage/5a8ca28f57103100104584db")
```

## Overall Questions

The DIA managers want to know what policies they could enact to increase the chances of on-time (or early) arrivals.

Are more flights delayed because of the carrier, weather, NAS (National Air System, aka the air traffic controllers), security issues, or aircraft late in arriving causing delays in departures?

## Team Plots

## Team Recommendation

## Individual Sections

## Eugene Miller
```{r, echo = FALSE, message = FALSE, warning = FALSE}
DENflights <- COflights %>%
  filter(ORIGIN == "DEN" | DEST == "DEN") %>%
  mutate(ARR_DELAY_LOGICAL = (ARR_DELAY >= 15))

ggplot(DENflights) +
  geom_smooth(mapping = aes(y = DEP_DELAY, x = LATE_AIRCRAFT_DELAY))
```

## Johnny Tamanaha
```{r}
uniq_dest <- DENflights %>%
  group_by(DEST) %>%
  summarize(total=n(), late=sum(DEP_DELAY>=15), prop=late/total) %>%
  filter(total>=200) %>%
  filter(rank(desc(prop)) < 10) %>%
  arrange(desc(prop))
ggplot(uniq_dest) +
  geom_col(mapping=aes(x=DEST, y=prop)) +
  labs(title="10 Highest Late Flight Proportions by Destination (originating from DEN)")+
  xlab("Destination")+
  ylab("Proportion of Late Flights")
```
```{r}
uniq_dest <- DENflights %>%
  group_by(DEST) %>%
  summarize(total=n(), late=sum(DEP_DELAY>=15), prop=late/total) %>%
  filter(total>=200) %>%
  filter(rank(desc(prop)) < 10) %>%
  arrange(desc(prop))
uniq_dest
```

Albany airport's late flight percentage is 10% greater than the second highest and 14% higher than the third highest late flight percentage. Also, Newark (at second place) is 4% higher than third place, which is significant because the next couple proportions don't differ by more than 1%. This indicates that there may be a correlation between the destinations ALB and EWR and departure delays. 

```{r}
carrier_delay <- DENflights %>%
  filter(CARRIER_DELAY>0)
ggplot(carrier_delay) +
  stat_binhex(mapping=aes(x=CARRIER_DELAY, y=DEP_DELAY)) +
  labs(title="Departure Delay vs. Carrier Delay", fill="# of Planes") +
  xlab("Carrier Delay (min)") +
  ylab("Departure Delay (min)") 
  
```
```{r}
late_total<- DENflights %>%
    filter(!is.na(DEP_DELAY))
  summarize(total=n(), late=sum(DEP_DELAY>=15), prop=late/total)
late_carrier <- DENflights %>%
  filter(CARRIER_DELAY >0) %>%
  summarize(total=n(), late=sum(DEP_DELAY>=15), prop=late/total)
```


Proportion of late flights from entire dataset: `r late_total$prop`.

Proportion of late flights from flights with aircraft delay: `r late_carrier$prop`.

Out of all the flights, 17% had departure delays that were 15 min or greater. If I filtered for flights with positive carrier delay (given carrier delay is greater than 0), that number jumps up to 89%. This suggests a correlation between carrier delay and delayed flights.

## Inidividual Contribution Summaries