---
title: "Lab 6: Team All Stars"
author: "Johnny Tamanaha, Emily Archambault, Eugene Miller, Kaiyuan Fan, Jingzhi Zhang"
date: "10/4/2019"
output: html_document
---

```{r, setup, message = FALSE, echo = FALSE, warning = FALSE}
library(tidyverse)
library(corrplot)
library(quantreg)
library(hexbin)
COflights <- read_csv("https://files.osf.io/v1/resources/3z5as4pej8/providers/osfstorage/5a8ca28f57103100104584db")
```

## Overall Questions

The DIA managers want to know what policies they could enact to increase the chances of on-time (or early) arrivals.

Are more flights delayed because of the carrier, weather, NAS (National Air System, aka the air traffic controllers), security issues, or aircraft late in arriving causing delays in departures?

## Team Plots

## Team Recommendation

## Individual Sections

## Eugene Miller
```{r, echo = FALSE, message = FALSE, warning = FALSE}
DENflights <- COflights %>%
  filter(ORIGIN == "DEN" | DEST == "DEN") %>%
  mutate(ARR_DELAY_LOGICAL = (ARR_DELAY >= 15))

ggplot(DENflights) +
  geom_smooth(mapping = aes(y = DEP_DELAY, x = LATE_AIRCRAFT_DELAY))
```
## Emily Archambault
```{r, echo=FALSE, message=FALSE, warning=FALSE}
DENVflights <- COflights %>% filter(ORIGIN == 'DEN' | DEST == 'DEN')
ggplot(DENVflights) + geom_smooth(mapping = aes(x = TAXI_OUT, y = ARR_DELAY), se=FALSE) + 
  labs(x = "Taxi Out Time", y = "Arrival Delay", title = "Plane Taxi Out Time vs Flight Arrival Delay")
```
Probability of a Flight Arriving Late, Given that it Had a Taxi Out Time >15 Mins:
```{r}
taxiandlate <- DENVflights %>% filter(ARR_DELAY >= 15, TAXI_OUT >= 15) %>% filter(!is.na(ARR_TIME)) %>% count()
taxilate <- DENVflights %>% filter(TAXI_OUT >= 15) %>% filter(!is.na(ARR_TIME)) %>% count()
prob <- taxiandlate/taxilate
```
probability = `r prob`

## Inidividual Contribution Summaries