---
title: "Lab 6: Team All Stars"
author: "Johnny Tamanaha, Emily Archambault, Eugene Miller, Kaiyuan Fan, Jingzhi Zhang"
date: "10/4/2019"
output: html_document
---

```{r, setup, message = FALSE, echo = FALSE, warning = FALSE}
library(tidyverse)
library(corrplot)
library(quantreg)
library(hexbin)
COflights <- read_csv("https://files.osf.io/v1/resources/3z5as4pej8/providers/osfstorage/5a8ca28f57103100104584db")
```

## Overall Questions

The DIA managers want to know what policies they could enact to increase the chances of on-time (or early) arrivals.

Are more flights delayed because of the carrier, weather, NAS (National Air System, aka the air traffic controllers), security issues, or aircraft late in arriving causing delays in departures?

## Team Plots

## Team Recommendation

## Individual Sections

## Eugene Miller

```{r, echo = FALSE, message = FALSE, warning = FALSE}
DENflights <- COflights %>%
  filter(ORIGIN == "DEN" | DEST == "DEN") %>%
  filter(!is.na(ARR_TIME))

ggplot(DENflights) +
  geom_smooth(mapping = aes(y = DEP_DELAY, x = WEATHER_DELAY)) + 
  labs(x = "Weather Delay (min)", y = "Departure Delay (min)", title = "Correlating Weather Delay and Departure Delay")
```

If the weather delay was at least 5 minutes, what's the probability of a departure delay?
```{r}
lateAircraft <- DENflights %>%
  filter(WEATHER_DELAY > 5)
lateAircraftDepDelay <- lateAircraft %>%
  filter(DEP_DELAY >= 15)
prob <- count(lateAircraftDepDelay)/count(lateAircraft)
```
It is: `r prob`

If a weather delay occurs then departure was more than likely delayed.

What's the relationship between month and departure delay?
```{r, echo = FALSE, message = FALSE, warning = FALSE}
ggplot(DENflights) + 
  geom_bar(mapping = aes(x = (DEP_DELAY >= 15), y = ..count../sum(..count..))) +
  facet_wrap(~MONTH) + 
  labs(x = "Was the plane's departure delayed?", y = "Proportion of Flights")
```

By month, whats the probability that a flight's departure is delayed?
```{r}
janFlights <- DENflights %>%
  filter(MONTH == 1)
janLate <- janFlights %>%
  filter(DEP_DELAY >= 15)
janProb <- count(janLate)/count(janFlights)

junFlights <- DENflights %>%
  filter(MONTH == 6)
junLate <- junFlights %>%
  filter(DEP_DELAY >= 15)
junProb <- count(junLate)/count(junFlights)

octFlights <- DENflights %>%
  filter(MONTH == 10)
octLate <- octFlights %>%
  filter(DEP_DELAY >= 15)
octProb <- count(octLate)/count(octFlights)
```
January: `r janProb`

June: `r junProb`

October: `r octProb`

This suggest that time of year can vary the likelyhood that a departure delay occurs significantly.

---

## Emily Archambault
```{r, echo=FALSE, message=FALSE, warning=FALSE}
DENVflights <- COflights %>% filter(ORIGIN == 'DEN' | DEST == 'DEN')
ggplot(DENVflights) + geom_smooth(mapping = aes(x = TAXI_OUT, y = ARR_DELAY), se=FALSE) + 
  labs(x = "Taxi Out Time", y = "Arrival Delay", title = "Plane Taxi Out Time vs Flight Arrival Delay")
```
Probability of a Flight Arriving Late, Given that it Had a Taxi Out Time >15 Mins:
```{r}
taxiandlate <- DENVflights %>% filter(ARR_DELAY >= 15, TAXI_OUT >= 15) %>% filter(!is.na(ARR_TIME)) %>% count()
taxilate <- DENVflights %>% filter(TAXI_OUT >= 15) %>% filter(!is.na(ARR_TIME)) %>% count()
prob <- taxiandlate/taxilate
```
probability = `r prob`
The plot and probability suggest there is a strong correlation between the length of time a plane spends taxi-ing out and the amount the arrival is delayed.

##Arrival Delay vs Month
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(DENflights) + geom_boxplot(mapping = aes(group=MONTH, x = MONTH, y = ARR_DELAY)) + scale_y_continuous(limits = c(-40, 30)) + labs(x = "Months (January - December)", y = "Arrival Delay", title = "Flight Month vs Arrival Delay")
```
Probability of a Flight Arriving Late, Given That it was in January
```{r}
janlate <- DENVflights %>% filter(ARR_DELAY >= 15, MONTH == 1) %>% filter(!is.na(ARR_TIME)) %>% count()
janflights <- DENVflights %>% filter(MONTH == 1) %>% filter(!is.na(ARR_TIME)) %>% count()
janprob <- janlate/janflights
```
probability = `r janprob`

Probability of a Flight Arriving Late, Given That it was in November
```{r}
novlate <- DENVflights %>% filter(ARR_DELAY >= 15, MONTH == 11) %>% filter(!is.na(ARR_TIME)) %>% count()
novflights <- DENVflights %>% filter(MONTH == 11) %>% filter(!is.na(ARR_TIME)) %>% count()
novprob <- novlate/novflights
```
probability = `r novprob`

The plot and probabilities suggest that the month of the year has an effect on the likelihood of a flight arriving late. Some months (such as January) have a much higher probability of having late flights than others (such as November).


---

## Johnny Tamanaha
```{r}
uniq_dest <- DENflights %>%
  group_by(DEST) %>%
  summarize(total=n(), late=sum(DEP_DELAY>=15), prop=late/total) %>%
  filter(total>=200) %>%
  filter(rank(desc(prop)) < 10) %>%
  arrange(desc(prop))
ggplot(uniq_dest) +
  geom_col(mapping=aes(x=DEST, y=prop)) +
  labs(title="10 Highest Late Flight Proportions by Destination (originating from DEN)")+
  xlab("Destination")+
  ylab("Proportion of Late Flights")
```
```{r}
uniq_dest <- DENflights %>%
  group_by(DEST) %>%
  summarize(total=n(), late=sum(DEP_DELAY>=15), prop=late/total) %>%
  filter(total>=200) %>%
  filter(rank(desc(prop)) < 10) %>%
  arrange(desc(prop))
uniq_dest
```

Albany airport's late flight percentage is 10% greater than the second highest and 14% higher than the third highest late flight percentage. Also, Newark (at second place) is 4% higher than third place, which is significant because the next couple proportions don't differ by more than 1%. This indicates that there may be a correlation between the destinations ALB and EWR and departure delays. 

```{r}
late_aircraft_delay <- DENflights %>%
  filter(LATE_AIRCRAFT_DELAY>0)
ggplot(late_aircraft_delay) +
  stat_binhex(mapping=aes(x=LATE_AIRCRAFT_DELAY, y=DEP_DELAY)) +
  labs(title="Departure Delay vs. Late Aircraft Delay", fill="# of Planes") +
  xlab("Late Aircraft Delay (min)") +
  ylab("Departure Delay (min)") 
  
```
```{r}
late_total<- DENflights %>%
  summarize(total=n(), late=sum(DEP_DELAY>=15), prop=late/total)
late_aircraft <- DENflights %>%
  filter(LATE_AIRCRAFT_DELAY >0) %>%
  summarize(total=n(), late=sum(DEP_DELAY>=15), prop=late/total)
```

Proportion of late flights from entire dataset: `r late_total$prop`.

Proportion of late flights from flights with aircraft delay: `r late_aircraft$prop`.

Out of all the flights, 17% had departure delays that were 15 min or greater. If I filtered for flights with positive late aircraft delay (given aircraft delay greater than 0), that number jumps up to 93%. This suggests a correlation between late aircraft delay and delayed flights.